---
title: "Half_life Estimation"
output: html_notebook
---


```{r}
set.seed(111)
```

### Generate some advertising data.
The vector GRP is a vector with length 200, which is the GRP from day 1 to day 200. \
Suppose this company doesn't purchase TV ads everyday, so on some days the GRP will be 0. A series of Bernouli random numbers are generate to determine if the day has TV ads. \
The actual GRP delivered won't be exact the same as the amount planned, so a series of Possion random numbers are generate to simulate he GRP. I use Possion to generate integers here since it's easier to verify if the calculation is correct, the real life data will be more complex.
```{r}
a <- rbinom(200,1,0.6)
b <- rpois(200,6)
GRP <- a*b
```

### Decay rate and half-life
Half-life is the lenght of time which will make the effectiveness of TV advertising decay to 50% of the original value. The effectiveness is represneted by TV GRP. The decay rate = 0.5 ^ (1/half-life). 
```{r}
rate <- 0.5 ^ (1/seq(1:70))
```

### Create a function to generate adstock
Since the effectiveness of TV ads has carryover effect, so we use adstock to quantified the effectiveness of TV ads today and the carryover effect from previous days.\
Adstock [i] is the adstock on day i. Adstock[1] = GRP[i] since there's no historical GRP.\
Adstock[2] = GRP[1]*decay_rate + GRP[2].\
Adstock[i] = Adstock[i-1]*decay_rate + GRP[i]
```{r}
adstock <- function(rate,grp){
  adstk <- rep(0,length(rep))
  adstk[1] <- grp[1]
  for (i in 2:length(grp)){
    adstk[i] <- rate*adstk[i-1] + grp[i]
  }
  return(adstk)
}
```

### Create Adstock with half-life from 1 day to 70 days (10 weeks).
Use a loop to create adstock with different half-life. This dataframe will be used to estimate to true half-life.
```{r}
m <- matrix(0,length(GRP),length(rate))

for (i in 1:length(rate)){
  m[,i] <- adstock(rate[i],GRP)
}

colnames(m) <- paste('adstock',1:70,sep="")

df <- data.frame(cbind(GRP,m))
```

